%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Diagnostic Technician III} % Job title
{Jabil Circuit} % Organization
{Zapopan, Jalisco} % Location
{July 2018 - February 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Reading and interpretation of log files provided by the test equipment.}
\item{Test and inspect electronic sub-assemblies and assemblies coming from production lines}
\item {Experience in ICT and FVT areas, performing debug test to the units in "Open \& short circuits" "Analog", "Boundary Scan Circuit", "Boundary Scan Interconnect", and so on.}
\item{I programmed firmware on boards and on individual Integrated Circuits.}
\item {Performed failure analysis at modular and component level on electronic boards, searching for the root cause of the failure and providing feedback to the ingineering involved.}
\item{I provided daily reports of all line issues.}	
\item{Knowledge and use of measuring tools and equipment like multimeters, signal generators, oscilloscope, LCR meter and X-Ray machine for the detection of internal short circuits in ICs and BGAs.}
\item{Ability to understand and use documentation, such as product schematic diagrams, component data sheets, BOMs, test tools, and technical procedures.}
\end{cvitems}
}

%------------------------------------------------    
\vspace{0.5cm}
\cventry
{Programmer Analyst I} % Job title
{Jabil Circuit} % Organization
{Zapopan, Jalisco} % Location
{February 2020 - March 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development and maintenance of applications in C Sharp with .NET framework and Visual Basic for different clients within the company.}
\item{Correction of errors detected in applications executed in Production environments (PRD).}
\item{Creation of documentation for the developed software.}
\item{Development of manuals and training materials.}
\item{Experience and development in Front-End technologies with HTML5, CCS and JavaScript using Angular.}
\item{Experience with relational databases with SQL Server and PostgreSQL.}
\end{cvitems}
}

%------------------------------------------------
\vspace{0.5cm}
\cventry
{Business System Analyst II} % Job title
{Jabil Circuit} % Organization
{Zapopan, Jalisco} % Location
{March 2023 - December 2024} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Constant communication with the Product Owner (PO) to shape the requirements of the final product (the application).}
\item{Translate the needs of the client or end user into user stories, tasks and acceptance criteria.}
\item{Use of DevOps to register user stories.}
\item{Preparation of documentation (BRD, FSD) to translate client information into technical requirements for the developer.}
\item{Identification of the functional and non-functional requirements of the application}
\item{Development of test cases designed to validate the functional and non-functional requirements of the system.}
\item {Performing UAT tests as required to validate the acceptance criteria.}
\item{Implementation of the application to the production environment.}
\item{Knowledge of the Software Development Lifecycle (SDLC), with the ability to work within defined roles.}
\item{Use of different Agile/Scrum methodologies.}
\end{cvitems} 
}

\vspace{0.5cm}
\cventry
{Business System Analyst III} % Job title
{Honda de México S.A. de C.V.} % Organization
{El Salto, Jalisco} % Location
{February 2025 - May 2026} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {I was in charge of the 'Customs Inventory Control' project to ensure compliance with Annex 24 of the General Foreign Trade Rules (RGCE). Under this regulation, the SAT requires IMMEX and VAT-certified companies to maintain an automated inventory control system to track the entry and exit of imported goods}
		\item {Managed the 'Volumetric Control' project, which is a mandatory system under Article 28 of the CFF, Annex 30. This system records and reports the inbound and outbound volumes of hydrocarbons and petroleum products to the SAT, ensuring traceability, legality, and proper tax compliance through the use of measurement equipment and specialized software.}
		\item {Contributed to the automation of the monthly VAT calculation, ensuring compliance with rule 2.7.1.32 of the 2024 Miscellaneous Fiscal Resolution (DOF). Enabled the system to process and store CFDIs (electronic invoices) on digital media in XML format, as required for all issuing taxpayers.}
		\item {I was in charge of the 'Fixed Asset Inventory Control System' project for the Celaya and Guadalajara plants. We modernized the labeling and identification process for the company's fixed assets, which enabled much better internal control and complete traceability for every single asset.}
	\end{cvitems} 
}
%------------------------------------------------



%------------------------------------------------

%------------------------------------------------

\end{cventries}